---
title: "Haar Wavelet Analysis"
author: "Zach Diener"
date: "June 4, 2015"
output: html_document
---
#Background Motivation
 I will be working to create code that will analyze a signal using Haar Wavelets. I am doing this in order to pick out features of signals that may be used as inputs into a neural network I will construct at a later point. 

#Attempt to model the Haar Analysis in Enhanced Brain Wave Analysis 
I am working to create code which may be applied to a wide variety of data. The goal is to have the function compute the averages and difference pertaining to said data set, then have the results displayed in a table. 

#Modeling the Averages function/table
```{r}

Row_1 = c(-12,0,12,16,12,0,-12,-16)
Averages=data.frame( Row_1)
n=length(Row_1)
i=c(1:(n))
fRow_1 <- function(Averages,Row_2){
  Row_2=c()
  for (i in 1:n){ 
    if(i==1){Row_2[1]=Row_1[1]*.5} 
    else {Row_2[i]=(Row_1[i-1]+Row_1[i])*.5}} 
  return(Row_2)
  unlist(Row_2)}
Averages$Row_2 <- fRow_1(Averages,Row_2)

fRow_2 <- function(Averages,Row_3){
  Row_3=c()
  Row_2=Averages$Row_2
  for (i in 1:n){ 
    if(i==1||i==2){Row_3[i]=Row_2[i]*.5} 
    #print(Row_3) 
    else {Row_3[i]=(Row_2[i-2]+Row_2[i])*.5}} 
  return(Row_3)}
Averages$Row_3 <- fRow_2(Averages,Row_3)

fRow_3 <- function(Averages,Row_4){
  Row_4=c()
  Row_3=Averages$Row_3
  for (i in 1:n){ 
    if(i==1||i==2||i==3||i==4){Row_4[i]=Row_3[i]*.5} 
    #print(Row_4) 
    else {Row_4[i]=(Row_3[i-4]+Row_3[i])*.5}} 
  return(Row_4)}
Averages$Row_4 <- fRow_3(Averages,Row_4)

Averages

```

#Modeling the Differences function/table
```{r}

Row_1 = c(-12,0,12,16,12,0,-12,-16)
fdRow_1 <- function(Averages,Row_1){
  dRow_1=c()
  for (i in 1:n){ 
    if(i==1){dRow_1[1]=Row_1[1]*-.5} 
    else {dRow_1[i]=(Row_1[i-1]-Row_1[i])*.5}} 
  return(dRow_1)
  unlist(dRow_1)}
dRow_1=fdRow_1(Averages,Row_1)
Differences=data.frame(dRow_1=c(dRow_1))

fdRow_2 <- function(Averages,Row_2){
  dRow_2=c()
  Row_2=Averages$Row_2
  for (i in 1:n){ 
    if(i==1||i==2){dRow_2[i]=Row_2[i]*-.5} 
    else {dRow_2[i]=(Row_2[i-2]-Row_2[i])*.5}} 
  return(dRow_2)
  unlist(dRow_2)}
dRow_2=fdRow_2(Averages,Row_2)
Differences$dRow_2<-dRow_2

fdRow_3 <- function(Averages,Row_3){
  dRow_3=c()
  Row_3=Averages$Row_3
  for (i in 1:n){ 
    if(i==1||i==2||i==3||i==4){dRow_3[i]=Row_3[i]*-.5} 
    else {dRow_3[i]=(Row_3[i-4]-Row_3[i])*.5}} 
  return(dRow_3)
  unlist(dRow_3)}
dRow_3=fdRow_3(Averages,Row_3)
Differences$dRow_3<-dRow_3
Differences
```
I believe that as my code stands various other sets of data may be analyzed regardless of their size. The first row of the averages must be input to begin this process. 

#Creating Heatmaps
```{r}
z=ncol(Differences)
j=c(1:(z))
DiffScaled<- as.matrix(Differences)

frow_labels <- function(j){(1/(2^j))*(1/sqrt(2))}
row_labels <-c(frow_labels(j))
row_labels<-round(row_labels,3)

heatmap.2(t(DiffScaled),
  main = "Features Heatmap",
  xlab = "Time",
  ylab = "Frequency",
  key=T, 
  keysize=1.5, 
  key.title = NA,
  symkey=TRUE,
  notecol="black",            
  density.info="histogram",     
  trace="none",               
  margins =c(12,9),            
  dendrogram="none",           
  Rowv = FALSE,
  Colv = FALSE,
  srtCol = 1,
  labRow = row_labels,
  cexRow = 1.0,
  breaks=50,
  adjCol = c(0.5,1)
  )       

```
